
\documentstyle[fp]{article}
\begin{document}

\newcommand{\hd}[1]{
\vspace*{0.2in} 
\noindent 
{\bf \Large #1}
\hspace{0.1in}
\vspace*{0.2in}}

\vspace{0.5in}


\begin{Large}
\begin{center}
Service Statement \\
\hspace{1mm} \\
Kevin Knight \\
\hspace{1mm} \\
December 2011
\end{center}
\end{Large}

\vspace{0.2in}

\noindent
In addition to teaching and leading a research group at USC, I have 
taken on these other roles:  

\hd{Conference, Journal, and Workshop Organization}

\noindent
I was Program Chair for the North American Association for 
Computational Linguistics (NAACL) conference in 2001.
I was also General Chair for the ACL conference in 2005.  
In between, I served as Area Chair for multilingual processing 
at numerous conferences.

I have served on several journal editorial boards, including {\em 
Computational Linguistics} (1999-2001), the {\em Journal of Artificial 
Intelligence Research} (1999-2001), {\em ACM Transactions on
Speech and Language Processing} (2004-2007), and {\em Machine Translation}
(2007-).

I was invited to lead the Johns Hopkins
summer workshop on language translation in 1999.
This six-week intensive workshop produced publicly-available software
that is still widely used by research groups today. 

In 2001, I co-organized (with Franz Josef Och and Jessie 
Pinkham) the first Association for Computational Linguistics (ACL)
workshop on data-driven approaches to language translation.  Annual
workshops on translation research have since been among the largest 
events associated with ACL conferences.

\hd{Research Program Management}

\noindent
I provided guidance to DARPA program managers Charles Wayne and Gary 
Strong, serving as Area Coordinator for Machine Translation in the 
DARPA TIDES research program (2001-2005).  In particular, I organized 
program-wide work on data resources to support translation research,
bridging between the research community and the Linguistic Data
Consortium at the University of Pennsylvania.

I was also active in the DARPA GALE program (2005-2010), one of
the largest R\&D programs at DARPA.  I coordinated language translation 
research in the AGILE research group, whose members include BBN, 
Cambridge University, Berkeley, University of Edinburgh, MIT, USC/ISI, 
and HKUST.

\hd{Executive Committees}

\noindent
I was elected to serve as President of ACL in 2011.  As President, 
I took the initiative to create a new ACL Fellows program, and
I headed the coordination committee for the 50th anniversary meeting 
of the ACL (Korea, 2012).
I also serve for five years on the ACL Executive Committee (2009-2013).
Previously, I was elected to serve as a Councillor for 
the Association for the Advancement of Artificial Intelligence (AAAI) 
from 2005 to 2007.

\hd{Commercialization}

\noindent
I co-founded Language Weaver, Inc. (2001) and serve as its Chief Scientist.  
Language Weaver has made numerous contributions
to the US national defense, including small-memory-footprint 
translation systems and broadcast monitoring systems, 
among other transitioned technologies.  Language Weaver
also allows companies like Dell, Adobe, Intel, and TripAdvisor to
provide high-accuracy customized translations to their users on the web.
The company was acquired by SDL plc in 2010.

\end{document}

